---
title: "Conversion Rate Optimization with A/B Testing: A Case Study on Udacity E-commerce Data"
author: "Thiruppathi"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

This project analyzes an A/B test for an e-commerce website.  
The goal is to determine whether **Control** has a higher conversion rate than **Treatment**.  

We use:
- **Conversion Rate** calculation  
- **Proportion Test** for hypothesis testing  
- **Visualization** to compare groups  

---

#Load and Explore the Dataset
```{r}
library(dplyr)
library(ggplot2)
Data<-read.csv("C:/Users/thiru/OneDrive/Desktop/AB_Test/ab_data.csv")
head(Data)
str(Data)
table(Data$group)
table(Data$landing_page)
```

#Summary of the Dataset
```{r}
Summary_Data<-Data %>% 
  group_by(group) %>% 
  summarise(Conversions=sum(converted),Visitors=n())
Summary_Data
```

#Conversion Rate of each group
```{r}
Conversion_Rate<-Data %>% 
  group_by(group) %>%
  summarise(
    Visitors=n(),
    Conversion=sum(converted),
    Conversion_Rate=(Conversion/Visitors)*100
  )
Conversion_Rate
```

#Proportion Test
```{r}
prop.test(x=Summary_Data$Conversions,n=Summary_Data$Visitors)
```

#Finding the Conversion Lift
```{r}
CR_Control<-Summary_Data$Conversions[Summary_Data$group=="control"]/
  Summary_Data$Visitors[Summary_Data$group=="control"]
CR_Treatment<-Summary_Data$Conversions[Summary_Data$group=="treatment"]/
  Summary_Data$Visitors[Summary_Data$group=="treatment"]

lift<-(CR_Treatment - CR_Control)/CR_Control *100
lift
```

#Visualize the result through Bar Chart
```{r}
ggplot(Conversion_Rate,aes(x=group,y=Conversion_Rate,fill = group))+
  geom_col(width=0.6) +
  geom_text(aes(label = paste0(round(Conversion_Rate,2),"%")),vjust=-0.5,size=3)+
  scale_y_continuous(labels = scales::percent_format())+
  labs(title="Conversion Rate by Group", y="Conversion Rate") +
  theme_bw()
```

#Results

Conversion Rate (control):  12.0 %

Conversion Rate (Treatment):  11.9 %

p-value from prop.test: 0.2182

#Conclusion

If p-value < 0.05, we reject H₀ and conclude that the difference in conversion rates is statistically significant.

In this test, Group **Control** shows higher conversion rates, and the improvement is not due to random chance.

**Control**  can be considered the better design for improving conversions.
